outlier_exploration

### 2025-05-07 Kyubin's Edit/KYUBIN_EDIT.qmd
lines 200 - 266 Continued replacing "sleep" with "sleep_test" Replaced "MAP" with "PP" variable in the predictors vector (line 203) After the VIF function is ran, the two variables with the highest R^2 Adj were Age and Quality of Sleep, so they were removed in the model_vif

# observation 264 has a leverage of 1

@@

# Define the full list of predictors (excluding the outcome)
predictors <- c("stress_level", "gender", "age", "quality_of_sleep",
                "physical_activity_level", "occupation", "bmi_category",
                "heart_rate", "daily_steps", "sleep_disorder", "MAP")

@@

# Apply the function to all predictors
aux_results <- do.call(rbind, lapply(predictors, get_aux_model_r2, data = sleep))

@@

# get rid of 3 highest aux r^2 adj and high vif scores: BMI and Quality
model_vif <- lm(sleep_duration ~gender + age + stress_level +  
                    physical_activity_level + occupation + 
                    heart_rate + daily_steps + 
                    sleep_disorder + MAP, data = sleep)

>>>>

# observation 264 has a leverage of 1 !

@@

# Define the full list of predictors (excluding the outcome)
predictors <- c("stress_level", "gender", "age", "quality_of_sleep",
                "physical_activity_level", "occupation", "bmi_category",
                "heart_rate", "daily_steps", "sleep_disorder", "PP")

@@

# Apply the function to all predictors
aux_results <- do.call(rbind, lapply(predictors, get_aux_model_r2, data = sleep_test))

@@

# get rid of 3 highest aux r^2 adj and high VIF scores: Age and Quality of sleep
model_vif <- lm(sleep_duration ~gender + bmi_category + stress_level +  
                    physical_activity_level + occupation + 
                    heart_rate + daily_steps + 
                    sleep_disorder + PP, data = sleep_test)
